On $K_2$-analogue of Serre problem for $\SL_4$

### 2018-04-27 paper.tex
Minor

\newtheorem{def}[lem]{Definition}
\Crefname{def}{Definition}{Definitions}
\newtheorem{example}[lem]{Example}
\Crefname{example}{Example}{Examples}

@@

@@

\subsection{Structure theorem for Steinberg groups}
The aim of section is to formulate sufficient conditions implying the main structure result for Steinberg groups

Let $\mu$ be a microweight of the root system $\Phi$. Denote by $N_\mu$
\begin{def}

\end{def}

>>>>

%\newtheorem{def}[lem]{Definition}
\Crefname{def}{Definition}{Definitions}
\newtheorem{example}[lem]{Example}
\Crefname{example}{Example}{Examples}

@@

\subsection{Steinberg groups and relative Steinberg groups}

\subsection{Rehmann-Soule theorem}

@@

\subsection{General structure theorem for Steinberg groups}
The aim of section is to formulate sufficient conditions implying the main structure result for Steinberg groups

Let $\mu$ be a microweight of the root system $\Phi$. Denote by $N_\mu$

\subsection{Construction of \texorpdfstring{$\sigma$}{sigma}-morphisms for $SL_4$}

\subsection{Proof of the theorem on \texorpdfstring{$\mathbb{P}^1$}{P1}-glueing for $K_2$}

\section{Applications}

\subsection{Bruhat--Tits buildings}

\subsection{\texorpdfstring{$A^1$}{A1}-invariance of the fundamental group}

\newpage
